Fiber Collision Correction Method for BOSS Power Spectrum

### 2015-03-31 fc_paper/fc_paper.tex
minor edit

Furthermore, we compare our method to the most common nearest-neighbor correction method and recent correction methods presented in \cite{Beutler:2014aa} and \cite{Gil-Marin:2014aa} to demonstrate that our method most successfully reproduces the true power spectrum at small scales and reliably at all scales for all the Las Damas, QPM, and Tiling mock catalogues. As an added advantage, our correction method can also be validated by actual data rather than only through the mock catalogues thereby making it's application to actual data further reliable.

>>>>

Furthermore, we compare our method to the most common nearest-neighbor correction method and recent correction methods presented in \cite{Beutler:2014aa} and \cite{Gil-Marin:2014aa} to demonstrate that our method most successfully reproduces the true power spectrum at small scales and most reliably at all scales for all the Las Damas, QPM, and Tiling mock catalogues. As an added advantage, our correction method can also be validated by actual data rather than only through the mock catalogues thereby making it's application to actual data further reliable.
